---
title: "Repr_Research"
author: "JAGUNS"
date: "21 juli 2016"
output: html_document
---
# Reproducible Research: Peer Assessment 1

## Load the Data.
```{r echo=TRUE} 
fileurl <- "https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip"
temp <- tempfile()
download.file(fileurl, temp)
unzip(temp)
unlink(temp)
activity <- read.csv("activity.csv", header=TRUE)
dim(activity)
```
### Loading an Processing the Data
```{r echo=TRUE}
ACT <- read.csv("activity.csv", header=TRUE)
```
### What is mean total number of steps taken per day?
### Plot Total Steps per Day

```{r echo=TRUE}
tbl <- with(ACT,tapply(steps,date,sum))
barplot(tbl)
title(ylab="Number of Steps",xlab="Date",main="Steps per Day")
```

### Mean and Median steps per day
```{r echo=TRUE}
totalStepsDay <- aggregate(steps ~ date,ACT,sum)
summary(totalStepsDay)
```

The average steps per day is `r summary(totalStepsDay)[11]`
The median steps per day is `r summary(totalStepsDay)[10]`

### What is the average daily activity pattern?
```{r echo=TRUE}
stepsInterval <- aggregate(steps ~ interval,ACT,mean)
m <- min(stepsInterval$steps[stepsInterval$steps != 0])
plot(stepsInterval$interval, log10(stepsInterval$steps + m),type="l",xlab="Intervals",ylab="Log10 of Steps")
title(main="Time Series Graph (Mean Steps per Interval)")
mxx <- which.max(stepsInterval[,2])
```

The Interval with the maximum steps is interval:`r mxx`

### Imputing missing values
```{r echo=TRUE}
nas <- sum(is.na(ACT$steps))
```
Number of NA's is: `r nas`

There are a number of packages that deal with imputing.
I have choosen the Hmisc package used in an earlier course.
```{r echo=TRUE}
library(Hmisc)
ACT1 <- ACT
ACT1$steps <- impute(ACT1$steps, mean)
agg1 <- aggregate(steps ~ date,ACT1,sum)
summary(agg1)
hist(agg1$steps,xlab="Total Steps per Day",ylab="Number of Days",main="Sum of Steps per Day")
```

The new average is: `r summary(agg1)[11]`
The new median is: `r summary(agg1)[10]`
Conclusion: The  mean and median are not changed,
because the NA's are imputed with the mean over all days.

### Are there differences in activity patterns between weekdays and weekends?
```{r echo=TRUE}
ACT1$date<- as.character(ACT1$date)
wday <- c("maandag","dinsdag","woensdag","donderdag","vrijdag")

for ( i in 1: dim(ACT1)[1]) {
  if (weekdays(as.Date(ACT1$date[i]))%in% wday){ ACT1$days[i]<-"weekdays"}
    else { ACT1$days[i]<-"weekend"}
}

ACT1 <- transform(ACT1, days=factor(days))
ACT1 <- transform(ACT1, date=factor(date))
str(ACT1)
aggr2 <- aggregate(steps ~ interval + days,ACT1,mean)
xyplot(steps ~ interval | days, data=aggr2,layout=c(1,2),type="l")
```



